Outline

### 2017-07-24 Scope.Rmd
Rename Outline.Rmd to Scope.Rmd

### Infrastructure provided to assist statistics educators
+ Take advantage of existing courses or build your own community course
+ Tutorials on how to build courses
+ Links to some github repositories

>>>>

### Infrastructure provided to assist statistics educators
+ Take advantage of existing courses or build your own community course
+ Tutorials on how to build courses
+ Use the template course files from 'Create a DataCamp Course' dialog
+ Links to some github repositories: most importantly 'datacamp/testwhat' to help with submission correctness tests
